---
title: "RWorksheet_urdas#4"
author: "Cindy Urdas"
date: "2022-11-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***1.	The table below shows the data about shoe size and height. Create a data frame.***\

```{r}
shoesize <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5,  5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
shoesize

height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.0, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
height

gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
gender

data.frame(shoesize,height,gender)

```
 
**a.	Describe the data.**\
The higher the height, the larger the shoe size, and according to the data frame, males have the highest height and the largest shoe size compared to females.\

**b.	Find the mean of shoe size and height of the respondents. Copy the codes and results.**\
```{r}
mean(shoesize)

mean(height)
```

**c.	Is there a relationship between shoe size and height? Why?**\
 	Yes, because the Higher the height, the greater the shoesize.\
 	
***Factors***\
A nominal variable is a categorical variable without an implied order. This means that it is impossible to say that ‘one is worth more than the other’. In contrast, ordinal variables do have a natural ordering.\
Example:\

## [1] M F F M\
## Levels: F M\


**2.	Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.**\
Consider data consisting of the names of months:\ "March","April","January","November","January", "September","October","September","November","August", "January","November","November","February","May","August",
"July","December","August","August","September","November","February","April")\

```{r}
months_vector <- c("March","April","January","November","January",   "September","October","September","November","August",  "January","November","November","February","May","August",
            "July","December","August","August","September","November","February","April")
factor_months_vector <- factor(months_vector)
factor_months_vector

```

**3.	Then check the summary() of the months_vector and factor_months_vector. | Interpret the results of both vectors. Are they both equally useful in this case?**\

```{r}
summary(months_vector,factor_months_vector)
```

***Create a vector and factor for the table below.***\

Direction	Frequency\
East	1\
West	4\
North	3\
Note: Apply the factor function with required order of the level.\
new_order_data <- factor(factor_data,levels = c("East","West","North"))\ print(new_order_data)\

```{r}
Direction <-c("East","West","North")
factor_Direction <-factor(Direction) 
factor_Direction

data <-c( 1, 4, 3)
factor_data <- factor(data)
factor_data


new_order_data <- factor(factor_data,levels = c("East","West","North")) 
print(new_order_data)
```

**5.	Enter the data below in Excel with file name = import_march.csv**\

***Figure 1: Excel File***\


a.	Import the excel file into the Environment Pane using read.table() function. Write the code.\

library(readxl)\
import_march_csv <- read_excel("D:/URDAS/import_march.csv.xlsx")\


b.	View the dataset. Write the code and its result.\
```{r}
library(readxl)
import_march_csv <- read_excel("D:/URDAS/import_march.csv.xlsx")
View(import_march_csv)
```
 









 	






